---
output:
  md_document:
    variant: markdown_github
---

# Purpose

Purpose of this work folder.

Ideally store a minimum working example data set in data folder.

Add binary files in bin, and closed R functions in code. Human Readable settings files (e.g. csv) should be placed in settings/


```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

#Introduction 
This is the root readme and details how I approached each question in the data science practical exam. Every question is in its own folder that contains the data and code relevant to that question. 

# Question 1 

This question is about the Covid-19 Pandemic. I first want to compare different regions' progression through the pandemic, hopefully comparing statistics like cases, deaths and/or vaccinations. Then, I look at how certain population characteristics (like smoking) affected pandemic progression. And, lastly, I consider whether increasing hospital capacity leads or lags ICU admissions. 

Let's see what information the dataset contains. 

## Data Exploration
### Dataset 1: covid_data_description

```{r}
# import dataset 1/3 
library(readr)
covid_data_description <- read_csv("C:/DatSci/Solution/20933835/Question1/data/Covid/covid_data_description.csv")

# let's look at the first few entries 
head(covid_data_description)

# This is a dataset of the descriptors used in 'owid_covid_data' 
```

This dataset contains descriptions of the columns in 'owid_covid_data' and I cannot do any interesting data manipulations with it. 

Let's load the next dataset. 

### Dataset 2: owid_covid_data 

```{r}
# import dataset 2/3 
library(readr)
owid_covid_data <- read_csv("C:/DatSci/Solution/20933835/Question1/data/Covid/owid-covid-data.csv")

# let's look at the first few entries 
head(owid_covid_data)
```

The data has many columns, which is not suitable to use in the tidyverse. I tidy the data by making a 'Metric' column that contains all the descriptors and names of metrics that were previously column names, and a 'Measure' column, that contains the value of measurement corresponding to the metric. I try to use this format and description throughout the project. 

```{r}
library(lubridate)

tidy_owid <- owid_covid_data %>% 
    gather(Metric, Measure, -date, -continent) %>% 
    na.omit() %>% #I want to delete rows with missing observations
    mutate(Year_Month = format(date, "%Y%B")) #I will probably want to work with data in months, not days, so I add another column for the 'year and month' to my tidy data. 
```

My computor cannot handle processing the tidy dataset so I need to make a smaller dataset so that my computor doesn't crash. I want to compare total cases and deaths by region. 

```{r}
regional_covid <- owid_covid_data %>% 
    group_by(continent, date) %>% 
    select(total_cases, total_deaths) %>% 
    na.omit %>% 
    ungroup

#check to see if we have all the continents and the spelling is correct
regional_covid %>% pull(continent) %>% unique

# we see we are missing antarctica, may have been na values that we omited?

# we can make this df more tidy 
regional_covid <- regional_covid %>% 
    gather(Metric, Measurement, -continent, -date)

#let's get total cases and deaths in each region
regional_covid <- regional_covid %>% 
    group_by(continent, Metric) %>% 
    mutate(Total_Region = sum(Measurement)) %>% 
    ungroup
```

```{r}
# i want to plot the total cases   
dfplotcases <- regional_covid %>% filter( Metric == "total_cases") %>% arrange(date)

# let's plot 
g <- dfplotcases %>% 
# Initialize the canvas:
ggplot() + 
# Now add the aesthetics:
geom_line(aes(x = date, y = Measurement, color = continent), alpha = 0.8 , linewidth = 1)

#let's adjust the labels and theme
g <- g + theme_bw() + theme(legend.position = "right") + labs(x = "Date", y= "Total Cases", title = "Total Covid Cases per Continent")

print(g)

# save the figure 
ggsave("C:/DatSci/Solution/20933835/Question1/Figures/Figure1.png", g, width = 6, height = 6, device = "png")

```

The graphs are cumulative... it may be better to look at "new cases". Again, I need to make a small dataset otherwise my computer will crash. 
```{r}
new_covid_data <- owid_covid_data %>% 
    group_by(continent, date) %>% 
    select(contains("new")) %>% 
    na.omit %>% 
    arrange(date) %>% 
    ungroup

small_new_covid_data <- new_covid_data %>% 
    select(date, continent, new_cases_per_million, new_deaths_per_million) %>% arrange(date) %>% 
    gather(Metric, Measurement, -date, -continent)
```

Let's plot the new cases per million 

```{r}
dfplot <- small_new_covid_data %>% filter( Metric == "new_cases_per_million") %>% arrange(date)
   
g2 <- dfplot%>% 
# Initialize the canvas:
ggplot() + 
# Now add the aesthetics:
geom_line(aes(x = date, y = Measurement, color = continent), alpha = 0.8 , linewidth = 1) 

#let's split the graphs up per country 
g2 <- g2 + facet_wrap(~continent)

#let's adjust the labels and theme
g2 <- g2 + theme_bw() + theme(legend.position = "right") + labs(x = "Date", y= "New Cases Per Million", title = "New Covid Cases per Continent")

print(g2)

# save the figure 
ggsave("C:/DatSci/Solution/20933835/Question1/Figures/Figure2.png", g2, width = 6, height = 6, device = "png")

```

Let's also graph the new deaths per million for each continent 

```{r} 
#I want to plot new deaths per million    
dfplotnewdeaths <- small_new_covid_data  %>% filter( Metric == "new_deaths_per_million") %>% arrange(date)
   
g3 <- dfplotnewdeaths%>% 
# Initialize the canvas:
ggplot() + 
# Now add the aesthetics:
geom_line(aes(x = date, y = Measurement, color = continent), alpha = 0.8 , linewidth = 1) 

#let's split the graphs up per continent 
g3 <- g3 + facet_wrap(~continent)

#let's adjust the labels and theme
g3 <- g3 + theme_bw() + theme(legend.position = "bottom") + labs(x = "", y= "New Deaths per Million", title = "New Covid Deaths per Continent")

print(g3)

# save the figure 
ggsave("C:/DatSci/Solution/20933835/Question1/Figures/Figure3.png", g3, width = 6, height = 6, device = "png")

```

Let's get total deaths and cases on one graph for each continent 
```{r}
pacman::p_load(lubridate)

dfplotnewdeaths <- small_new_covid_data  %>% filter( Metric == "new_deaths_per_million") %>% arrange(date) 

g4 <- g2 + geom_line(data = dfplotnewdeaths, aes(date, Measurement, color=continent), colour = "steelblue", alpha = 0.3) + geom_label(data = dfplotnewdeaths %>% 
    filter(date == last(date)), aes(date, Measurement, label = continent), 
    size = 3, alpha = 0.1) + 
    geom_label(data = dfplot %>% filter(date == last(date)), 
    aes(date, Measurement, label = continent), size = 3, alpha = 0.1)

print(g4)

# save the figure 
ggsave("C:/DatSci/Solution/20933835/Question1/Figures/Figure4.png", g4, width = 6, height = 6, device = "png")
```
I didn't quite get that to work... Let's move on 

Other covid questions: how does poverty/ smoking/ elderly pop affect patterns in severity 

How did increasing hospitalisations lag or lead icu admissions (plot hosp and icu admissions on one graph to show lag or lead?)

```{r}
#let's collect the garbage, my computer is struggling
gc()
```

### Dataset 3: Deaths_by_cause

'Deaths_by_cause' provide additional insights into the causes of death for before the Covid outbreak. Let's investigate the dataset.

```{r}
# import dataset 3/3 
library(readr)
Deaths_by_cause <- read_csv("C:/DatSci/Solution/20933835/Question1/data/Covid/Deaths_by_cause.csv")

#let's look at the first few entries 
head(Deaths_by_cause)
```

I want to make this data tidy. I want one 'Cause of Death' column that gathers all the different types of deaths, and a 'Quantity' column that gives the number of deaths for each cause of death. I am not interested in the deaths that have missing quantities so I delete these entries from the tidy dataset.

```{r}
tidy_Deaths_by_cause <- Deaths_by_cause %>% 
    gather(Cause_of_Death, Quantity, -Year, -Entity, -Code) %>%
    arrange(Year) %>% 
    na.omit
```

What years are the data for? 

```{r}
tidy_Deaths_by_cause %>% pull(Year) %>% unique
```

I am only interested in the deaths occuring in 2019, the year before the pandemic, so I filter out all data for dates before 2019.

```{r}
deaths_2019 <- tidy_Deaths_by_cause %>% 
 filter(Year >= 2019)

#check that there are only entries for 2019 
deaths_2019 %>% pull(Year) %>% unique
```

Let's check that the descriptors in 'cause of death' is appropriate, and what the unique causes of death are that we're looking at. 

```{r}
deaths_2019 %>% pull(Cause_of_Death) %>% unique
```

There are 31 causes of death. 

Let's summarise the causes of death for each continent in a table. 
```{r}
# Deaths before covid:

```

# Question 2 
This question is about the weather in mid parts of the UK.  

I start by exploring the dataset. The data folder contains an information document which specifies the UKMonthly_detailed column information. 

## Data Exploration
```{r}
# import dataset 1/2
library(readr)
london_weather <- read_csv("C:/DatSci/Solution/20933835/Question2/data/London/london_weather.csv")

# Let's look at the first few entries 
head(london_weather)
```

This dataset is less detailed than the second, focusing on London, which is not in the mid parts of the UK, but rather on the South Eastern side. Hence, this dataset will not convince anyone that the mid-UK areas have poor weather. 

The second dataset is more detailed and focuses on the mid parts of the UK, so we will use this dataset. It is accompanied by a pdf that defines the column names. 

```{r}
# import dataset 2/2
library(readr)
UKMonthly_Detailed <- read_csv("C:/DatSci/Solution/20933835/Question2/data/London/UKMonthly_Detailed.csv")

# Let's look at the first few entries 
head(UKMonthly_Detailed)
```

Based on the info doc, I don't want any of the variables called 'attributes', so I drop them from the dataset.  

```{r}
weather <- UKMonthly_Detailed %>% 
    select(!contains("ATTRIBUTES"))
```

How many names and stations are there? I want to know which areas in the central UK we can consider.

```{r}
weather %>% pull(NAME) %>% unique
weather %>% pull(STATION) %>% unique
```

The weather data is all for the same station/area, so we can drop these datapoints as they are redundant. 

```{r}
weather <- weather %>% select(!contains("STATION")) %>% select(!contains("NAME"))
```

Now I want to make the data tidy by collecting all columns under 'Metric' where their values are capture in 'Measure.' I want to delete any rows with missing observations. 

```{r}
tidy_weather <- weather %>% 
    gather(Metric, Measure, -DATE) %>% 
    na.omit %>% 
    arrange(DATE)
```

The climate has changed over time, hence I do not want to look at the weather going all the way back to the 1800s. Let's only consider the weather for the last 50 years (approximately). This means we consider the weather from about the 1970's onwards. 

```{r}
tidy_weather <- tidy_weather %>% 
    arrange(DATE) %>% 
    filter(DATE >= 1970)
```

What aspects of the weather can we consider? Let's investigate what's recorded in 'Metric' and look up the definitions in the info doc. 

```{r}
tidy_weather %>% pull(Metric) %>% unique
```
Measuring latitude, longitude, elevation is not interesting. 
We can look at temperatures (extremes and averages). 

It could be interesting to look at the temperetures occuring in each season over the last 50 years. Let's make seasons. The seasons occur in the following months in the UK: 

Spring =  March - May 
Summer = June - August 
Autumn = Sep - Nov 
Winter = Dec - Feb 

```{r}
# add a 'season' column that contains the four seasons that correspond to the month 

tidy_weather_seasons <- tidy_weather %>% 
    mutate(Season = ifelse(c(grepl("01|02|12", DATE)), "Winter", 
                           ifelse(c(grepl("03|04|05", DATE)), "Spring", 
                                  ifelse(c(grepl("06|07|08", DATE)), "Summer", 
                                         ifelse(c(grepl("09|10|11", DATE)), "Autumn", NA)))))

# Let's check that we have all the seasons and no other entries in seasons 
tidy_weather_seasons %>% pull(Season) %>% unique
```
 
Let's plot the minimum temperatures for each season over the last 50 years

```{r}
min_temp <- tidy_weather_seasons %>% 
    group_by(Season) %>% 
    filter (Metric == "TMIN") %>% 
    ungroup

g5 <- min_temp %>% 
    ggplot()+ 
    geom_line(aes(x=Season, y=Measure, color=Season), alpha=0.8, linewidth=1)+ 
    theme_classic()+ theme(legend.position = "right") +labs(x="Season", y="Temperature in Celsius", title = "Minimum Temperatures per Season for the last 50 Years")

print(g5)

# save the figure 
ggsave("C:/DatSci/Solution/20933835/Question2/Figures/Figure1.png", g5, width = 6, height = 6, device = "png")

```

This would be better as a boxplot. 

```{r}
min_temp <- tidy_weather_seasons %>% 
    group_by(Season) %>% 
    filter (Metric == "TMIN") %>% 
    ungroup

g6 <- min_temp %>% 
    ggplot()+ 
    geom_boxplot(aes(x=Season, y=Measure, color=Season), alpha=0.8)+ 
    theme_classic()+ theme(legend.position = "right") +labs(x="Season", y="Temperature in Celsius", title = "Summary of Minimum Temperatures per Season for the last 50 Years")

print(g6)

# save the figure 
ggsave("C:/DatSci/Solution/20933835/Question2/Figures/Figure2.png", g6, width = 6, height = 6, device = "png")

```

Let's make a similar boxplot of the maximum temperatures for each season.

```{r}
max_temp <- tidy_weather_seasons %>% 
    group_by(Season) %>% 
    filter (Metric == "TMAX") %>% 
    ungroup

g7 <- max_temp %>% 
    ggplot()+ 
    geom_boxplot(aes(x=Season, y=Measure, color=Season), alpha=0.8)+ 
    theme_classic()+ theme(legend.position = "right") +labs(x="Season", y="Temperature in Celsius", title = "Summary of Maximum Temperatures per Season for the last 50 Years")

print(g7)

# save the figure 
ggsave("C:/DatSci/Solution/20933835/Question2/Figures/Figure3.png", g7, width = 6, height = 6, device = "png")
```

Let's have a closer look at the temperatures... specifically the number of days that the min or max temperature is above or below a specific value. 

I want to use a description that is easier to understand. 
They are as follows: 

DT00 = no of days that min temp less -17,8 = Disgustingly Cold 
DT32 = no of days that min temp less 0 = SUPER Cold 
DX32 = no of days that max temps less 0 = Very Cold
DX79 = no of days that max temps less 21,1 = Cold
DX90 = no of days that max temps greater 32,2 = Hot 

```{r}
tidy_weather_seasons <- tidy_weather_seasons %>%
    mutate(temp = ifelse(c(grepl("DX32", Metric)), "Very Cold",
                         ifelse(c(grepl("DX70", Metric)), "Cold", 
                                ifelse(c(grepl("DX90", Metric)), "Hot", 
                                       ifelse(c(grepl("DT32", Metric)), "SUPER Cold", 
                                              ifelse(c(grepl("DT00", Metric)), "Disgustingly Cold", NA))))))
   
```

I want to see how many cold, super cold, etc days there were last year. 

```{r}
#what was the temp like in the last year
temp <- tidy_weather_seasons %>% 
    group_by(temp) %>% 
    na.omit %>% 
    select(-Metric) %>%
    filter(DATE>2022-03)
    ungroup

g8 <- temp %>%
    ggplot()+ 
    geom_col(aes(x=temp, y=Measure, color=temp), alpha=0.8, linewidth=1)+ 
    theme_bw() + labs(x="Weather for the Day", y="Number of Days", title = "The Weather in 2022")

print(g8)

#as you can see, it is cold and super cold most of the time, with very few hot days  

# save the figure 
ggsave("C:/DatSci/Solution/20933835/Question2/Figures/Figure4.png", g8, width = 6, height = 6, device = "png")
```

But what is the average temperature like in each season? A boxplot of each season can show the average min, max and median temperatures, as well as outliers. 

```{r}
tavg <- tidy_weather_seasons %>% 
    group_by(Season) %>% 
    filter(Metric == "TAVG") %>% 
    ungroup 

g9 <- tavg %>%
    ggplot()+ 
    geom_boxplot(aes(x=Season, y=Measure, color=Season), alpha=0.8, linewidth=1)+
    theme_bw() + labs(x= "Season", y="Average Temperature in Celsius", title="A Summary of the Average Seasonal Temperatures")

print(g9)

# save the figure 
ggsave("C:/DatSci/Solution/20933835/Question2/Figures/Figure5.png", g9, width = 6, height = 6, device = "png")
    
```

make a table with ave temps for each season

```{r}
#again, let's collect the garbage before we start a new question for the sake of my poor computer
gc()
```

# Question 3

This question is about music. More specifically it is about the longevity and musical progression of two bands; Coldplay and Metallica. 

I start by exploring the datasets. Along with the data is a text file containing the definitions used in the datasets. 

## Data Exploration
### Dataset 1: Broader_Spotify_Info

```{r}
# Import dataset 1/3 
library(readr)
Broader_Spotify_Info <- read_csv("C:/DatSci/Solution/20933835/Question3/data/Coldplay_vs_Metallica/Broader_Spotify_Info.csv")

# Let's look at the first few entries 
head(Broader_Spotify_Info)
```

I want to first investigate the longevity and progression of Coldplay and Metallica, so will not manipulate the broader spotify data just yet. However, I could filter the spotify data for each band as follows. 

```{r}
spotify_cold_met <- Broader_Spotify_Info %>% 
    filter("Coldplay" %in% artist)

# we want to tidy this dataset 
tidy_spotify_cold_met <- spotify_cold_met %>% 
    gather(Attribute, Measure, -year) %>% 
    na.omit
```

This is just as a reminder to myself for when I go through the README again later. 

Let's load the other datasets. 

### Dataset 2 and 3: Coldplay and Metallica
####Coldplay 

Let's import and have a look at the coldplay dataset. 

```{r}
# Import dataset 2/3 
library(readr)
Coldplay <- read_csv("C:/DatSci/Solution/20933835/Question3/data/Coldplay_vs_Metallica/Coldplay.csv")

# Let's look at the first few entries
head(Coldplay)
```

Let's tidy the Coldplay dataset (using 'Metric' and 'Measure' in the same way as the previous questions) and delete any rows with missing observations.

```{r}
tidy_coldplay <- Coldplay %>% 
    gather(Metric, Measure, -name, -release_date) %>% 
    arrange(release_date) %>% 
    na.omit
```

#### Metallica
Let's import and have a look at the Metallica dataset. 

```{r}
# Import dataset 3/3 
library(readr)
metallica <- read_csv("C:/DatSci/Solution/20933835/Question3/data/Coldplay_vs_Metallica/metallica.csv")

# Let's look at the first few entries 
head(metallica)
```

Let's tidy the Metallica dataset (using 'Metric' and 'Measure' in the same way as the previous questions) and delete any rows with missing observations.

```{r}
tidy_metal <- metallica %>% 
    gather(Metric, Measure, -name, -release_date) %>% 
    arrange(release_date) %>% 
    na.omit
```

The practical suggests making a boxplot for each band, showing the popularity of each album using box plots. I will start my analysis by replicating these boxplots and will handle each band separately. 

Let's start with Coldplay. 
The data relevant to the boxplot is 'popularity' and 'album_name'

```{r}
coldplay_pop <- Coldplay %>% 
    select(album_name, popularity, release_date) %>% 
    na.omit

g10 <- coldplay_pop %>% arrange(release_date) %>% 
    ggplot()+
    geom_boxplot(aes(x=album_name, y=popularity, color=album_name))+
    theme_bw() +labs(x="Album", y="Popularity", title = "Coldplay Popularity by Album") +theme(legend.position = "none")

print(g10)

# save the figure 
ggsave("C:/DatSci/Solution/20933835/Question3/Figures/Figure1.png", g10, width = 6, height = 6, device = "png")

```

I do the same thing for metallica... but I run into an issue with knitting here so I comment this chunk out for now... it would be nice if the issue could be fixed 
```{r}
 metal_pop <- metallica %>% 
     select(album, popularity, release_date) %>% 
     na.omit
# 
# g11 <- metal_pop %>% arrange(release_date) %>% 
#     ggplot()+
#     geom_boxplot(aes(x=album, y=popularity, color=album))+
#     theme_bw() +labs(x="Album", y="Popularity", title = "Metallica Popularity by Album") +theme(legend.position = "none")
# 
# print(g11)
# 
# # save the figure 
# ggsave("C:/DatSci/Solution/20933835/Question3/Figures/Figure2.png", g11, width = 6, height = 6, device = "png")
#     
```

We want to compare the bands on a like-for-like basis. We can start by comparing their popularity since we are already working with the popularity metric. 

I want to know how the bands popularity scores compare to each other on average, so we I can advise music producers as to which band's "recipe to success" they should rather follow. We can then investigate what made the one band more popular than the other. 

### Popularity 

First, let's make functions that calculate the average popularity for each band. 

```{r}
# function to return Coldplay's average popularity
mean_coldplay_popularity_calculator <- function(){
    x = coldplay_pop
    ave_pop = mean(coldplay_pop$popularity)
    
    return(print(ave_pop))
    
}

#I want to save the average popularity to use for comparison later
Coldplay_Ave_Popularity <- mean_coldplay_popularity_calculator()


# function to return Metallica's average popularity
mean_metallica_popularity_calculator <- function(){
    x = metal_pop
    ave_pop = mean(metal_pop$popularity)
    
    return(print(ave_pop))
    
}

#I want to save the average popularity to use for comparison later
Metallica_Ave_Popularity <- mean_metallica_popularity_calculator()

```

Now we can directly compare the bands' average popularities. I would like to visualise the difference in average popularity, so I make a new data frame with the popularity scores and I tidy it so I can more easily use ggplot2. 

```{r}
#I want to put both bands' average popularity scores in one data frame 
popularity = data.frame(Metallica_Pop = c(Metallica_Ave_Popularity), 
                        Coldplay_Pop = c(Coldplay_Ave_Popularity)) 

#tidy the data frame so its easier to plot 
popularity <- popularity %>% 
    gather(Band, Ave_Pop_Score)

#plot average popularity scores 
g12 <- popularity %>% 
    ggplot()+
    geom_count(aes(x=Band, y=Ave_Pop_Score, color=Band))+ 
    theme_bw() + labs(x= "Band", y= "Average Popularity", title="Average Popularity for Coldplay and Metallica") + theme(legend.position = "none")

print(g12)

# save the figure 
ggsave("C:/DatSci/Solution/20933835/Question3/Figures/Figure3.png", g12, width = 6, height = 6, device = "png")

```

We can see that, on average, Coldplay is much more popular than Metallica. But how much popular exactly? Let's write a function that will do this calculation and tell me in a sentence what the result is. 

```{r}
# make a function returning the percentage of how much more popular coldplay is than metallica, and round off to 2 decimal places 

percent_more_pop <- function(){
    x = Coldplay_Ave_Popularity 
    y = Metallica_Ave_Popularity
    z = round(((x-y)/x)*100, 2)
    
#I want the function to return a sentence that tells me the result 
    return(glue::glue("Coldyplay is {z} % more popular than Metallica on average"))
}

percent_more_pop()
```

Why is Coldplay so much more popular? 

```{r}
#let's collect the garbage before we start the next question
gc()
```

# Question 4 
This question is about streaming services, and what features make streaming platforms more or less popular. The data is on Netflix only, so I need to extrapolate what features would be good to have in a streaming service, and what features would not be good to have in a streaming service from one platform's data. 

Note for the column definitions: IMDb (an abbreviation of Internet Movie Database) is an online database of information related to films, television series, home videos, video games, and streaming content online – including cast, production crew and personal biographies, plot summaries,
trivia, ratings, and fan and critical reviews.

I start by exploring the datasets. 

## Data Exploration
### Dataset 1: credits
```{r}
# Import dataset 1/2 
library(readr)
credits <- read_csv("C:/DatSci/Solution/20933835/Question4/data/netflix/credits.csv")

# Let's look at the first few entries 
head(credits)
```

Let's make it tidy, following the same method as in the preceding questions, and deleting any rows with missing values. 

```{r}
tidy_credits <- credits %>% 
    gather(Metric, Measure, -name) %>% 
    arrange(name) %>% 
    na.omit
```

The credits describe which actors starred in which productions, and who the director was, etc, which could contribute to the production's popularity. Keep this in mind for later. Let's see if we can get a measure of popularity in the other dataset to work with first. 

Let's load the other dataset.

### Dataset 2: titles
```{r}
# Import dataset 2/2 
library(readr)
titles <- read_csv("C:/DatSci/Solution/20933835/Question4/data/netflix/titles.csv")

# Let's look at the first few entries 
head(titles)
```

We can see that this dataset contains popularity scores and imdb scores, so we'll work with this data first. 

Let's make it tidy, following the same method as in the preceding questions, and deleting any rows with missing values. 

```{r}
tidy_titles <- titles %>% 
    gather (Metric, Measure, -release_year, -title) %>% 
    arrange(release_year) %>% 
    na.omit
```

What kind of productions are more popular? Let's compare popularity by age certification i.e. should streaming services upload more PG or more R rated productions, for example. Let's compare by tmdb popularity. 

```{r}
age_pop <- titles %>% 
    select(age_certification, imdb_score, tmdb_popularity) %>% 
    na.omit()

# I want the average popularity for R rated movies, so let's isolate R
R_pop <- age_pop %>% 
    group_by(age_certification) %>% 
    filter(age_certification == "R") %>% 
    ungroup

#now I can make a function that calculates the average imdb scores for R rated productions 
R_pop_ave_imdb_score <- function(){
    x= R_pop
    ave_R_imdb_score = mean(R_pop$imdb_score)
    
    return(print(ave_R_imdb_score))
    
}

#I want to save the average popularity to use for comparison later
ave_R_pop_imdb_score <- R_pop_ave_imdb_score()

#now I can make a function that calculates the average tmdb popularity scores for R rated productions 
R_pop_ave_tmdb_pop <- function(){
    x= R_pop
    ave_R_tmdb_pop = mean(R_pop$tmdb_popularity)
    return(print(ave_R_tmdb_pop))
    
}

#I want to save the average popularity to use for comparison later
ave_R_pop_tmdb_pop <- R_pop_ave_tmdb_pop()

```

Now I want to do the same for the other age certifications

# Question 5
This question is about... 
I start by exploring the dataset. 
## Data Exploration
```{r}
# Import dataset 1/2 
library(readr)
googleplaystore_user_reviews <- read_csv("C:/DatSci/Solution/20933835/Question5/data/googleplay/googleplaystore_user_reviews.csv")

# Let's look at the first few entries 
head(googleplaystore_user_reviews)
```

Let's make it tidy 
```{r}
tidy_reviews <- googleplaystore_user_reviews %>% 
    gather(Attribute, Measure, -App) %>% 
    arrange(App) %>% 
    na.omit
```

Load the other dataset 
```{r}
# Import dataset 2/2 
library(readr)
googleplaystore <- read_csv("C:/DatSci/Solution/20933835/Question5/data/googleplay/googleplaystore.csv")

# Let's look at the first few entries 
head(googleplaystore)
```

Let's make it tidy 
```{r}
tidy_playstore <- googleplaystore %>% 
    gather(Attribute, Measure, -App) %>% 
    arrange(App)
    na.omit
```

I ran out of time to do more data wrangling. I prioritized getting everything to knit correctly and submitting on time. 


